---
title: "P-hacking COVID-19"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

Here is our code of COVID-19 challanges.

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read the data


```{r read data and exclude the unreasonable data}
library(utils)
data <- read.csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", na.strings = "", fileEncoding = "UTF-8-BOM")
data <- data[data$cases>=0,]
head(data)
```

## Add another colum called number of character in a country name 

(such as USA have 3 characters, Chile have 5 characters and so on) 

```{r pressure, echo=FALSE}
data$number <- nchar(data$countriesAndTerritories)
```

Then we did the linear regression, since the bias of confirmed cases are too big. Here we used log(cases+1) to made the graph clearer.
```{r}
model <- glm(log(cases+1)~number,data= data)
summary(model)
```

```{r plot the conclusion}
library(ggrepel)
library(dplyr)
p1 <- data %>%
  ggplot()+
  aes(x=number,y=log(cases+1))+
    geom_point()+
    geom_abline(color='red',intercept=coef(model)[1],slope=coef(model)[2])+
  labs(x='Number of the characters in the country')

p1
```

## Conclusion
Supersingly, we found out that the length of the countries' name do have an significant effect on the daily case of COVID-19. The shorter the length of the countries' names, the higher COVID-19 cases they have. This could be explained by the fact that places with fewer characters are more well-known. People tends to travel to those more often thus increased the amount of the COVID-19 cases. To be honest, the sample size of the data are quite large so every variables could be possibly high-correlated to the confirmed case. We should then explored more about the mechanism behind the length of the countries' name to proof whether our finding is true.
